Analyzing tweets to detect social media events

### 2020-05-18 Rmd/jse-2019-ms.Rmd
deleted a mentoring paragraph

Mentoring in the work place and in higher education has many 
benefits, including improving 1) students' development as thinkers and scholars, 2) confidence in their 
own abilities, 3) integration into the campus community,
and 4) interest in graduate training [@baker2010beyond;@higgins2001reconceptualizing].

@@

**PLACE TWEET JSON HERE**
### Parsing text of tweets

We used functions from the `rtweet` package to parse tweet JSON into a data frame. From there, we used `tidytext` R package 
functions to break the tweet text into individual words. We discarded commonly used "stop words" 
and emojis.

>>>>

@@

### Parsing text of tweets

We used functions from the `rtweet` R package to parse tweet JSON into a data frame. From there, we used `tidytext` R package 
functions to break the tweet text into individual words. We discarded commonly used "stop words" 
and emojis.
